A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-03-08 survey.tex
Adding my bio

>>>>

\begin{IEEEbiographynophoto}{Alberto Uriarte}
received the B.S. degree in Computer Science from Autonomous University of Barcelona (UAB), Spain, in 2006 and the M.S. degree in Computer Vision and Artificial Intelligence from Autonomous University of Barcelona (UAB), Spain, in 2011. He is currently pursuing the Ph.D. degree in computer science at Drexel University. His research interest includes game AI, RTS games, multiagents systems, procedural content generation, computational geometry, machine learning and drama management.  
\end{IEEEbiographynophoto}
